Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-09-12 tex/scam/sparsistency.tex
minor edits

\begin{theorem}[Controlling false positives]
\label{thm:false_positive}
Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
and suppose 
\begin{equation}
\lambda_n \geq 8 s_0 \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
\end{equation}  
Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
S^c$, and for all $i'=1,\ldots, n$,
\begin{equation}
\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
\end{equation}
and for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\eqref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\eqref{opt:alternate_opt_concave} are zero. 
\end{theorem}

>>>>

\begin{theorem}[Controlling false positives]
\label{thm:false_positive}
Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
and suppose 
\begin{equation}
\lambda_n \geq 8 s_0 \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
\end{equation}  
Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
S^c$, and for all $i'=1,\ldots, n$,
\begin{equation}
\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
\end{equation}
and for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero. 
\end{theorem}
